### 2013-06-20 trunk/network-science/paper.tex
8

\documentclass[12pt,abstract=true]{scrartcl}

%<<< Preamble
\usepackage{tikz}
\usepackage{array}
\usepackage{pifont}
\usepackage{engord}
\usepackage{listings}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage{fancyvrb}
\usepackage{multicol}
\usepackage{pgfplots}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage[plain]{fancyref}
\usepackage[unicode]{hyperref}
\usepackage{graphicx,tabularx}
\usepackage[shortlabels]{enumitem}
\usepackage[retainorgcmds]{IEEEtrantools}
\usepackage{amsmath,amssymb,amsthm,amscd,amstext}
\usepackage{mathtools}
\usepackage{exscale}
\usepackage{relsize}
\usepackage{mathrsfs}

@@

@@

\begin{center} %<<< Title
	\Large \textbf{\textsf{
		Metrics and Algorithms for Evolving Social Networks}} \\[1.5em]
	\small
		Pufan He\upper{1}, Yichao Zhou\upper{2}, Qiwei Feng\upper{3},
		Yu Yan\upper{4}, Qingyang Li\upper{5} and Xin Xing\upper{6}\\[1em]
	\begin{tabular}{*{3}{>{\centering}p{.25\textwidth}}}
		\upper{1}\href{mailto:hpfdf@126.com}{hpfdf@126.com} &%
		\upper{2}\href{mailto:broken.zhou@gmail.com}{broken.zhou@gmail.com} &%
		\upper{3}\href{mailto:gdfqw93@163.com}{gdfqw93@163.com} \tabularnewline

		\upper{4}\href{mailto:whyvine@hotmail.com}{whyvine@hotmail.com} &
		\upper{5}\href{mailto:591527324@qq.com}{591527324@qq.com} &
		\upper{6}\upper{1}\href{mailto:823291634@qq.com}{823291634@qq.com}
	\end{tabular} \\[1em]

	\normalsize IIIS, Tsinghua University \\[1.5em]
\end{center} \par %>>>

\begin{abstract}
We address the dynamic properties of typical social networks, in which person
is considered as vertex while relation is considered as edge. We suppose the
evolution of a social network overtime only includes bidirectional new
connections between existing or newly created nodes, and we assume the graph
will evolve as a typical social network. We study the centrality and activity
metrics for nodes in such graphs by regulate a series of reasonable properties
the metrics should satisfy. We then formally define our metrics and give their
mathematical analysis. We have developed a practical based framework to
maintain the evolving network and the algorithm to compute our metrics with
preferable time and space consumption, including historical queries. Finally,
we put the result of experiment with a couple of authentic data.

\smallskip
\noindent \textbf{Keywords.} social network, dynamic graph, centrality,
activity, algorithm.
\end{abstract}

\section{Introduction}
social network 
\section{}
\section{}
\section{Conclusion}
\nocite{*}
\bibliography{paper.bib}
\end{document}

>>>>

\documentclass[a4,12pt,abstract=true]{scrartcl}

%<<< Preamble
\usepackage{tikz}
\usepackage{array}
\usepackage{pifont}
\usepackage{engord}
\usepackage{listings}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage{fancyvrb}
\usepackage{multicol}
\usepackage{pgfplots}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage[plain]{fancyref}
\usepackage[unicode]{hyperref}
\usepackage{graphicx,tabularx}
\usepackage[shortlabels]{enumitem}
\usepackage[retainorgcmds]{IEEEtrantools}
\usepackage{amsmath,amssymb,amsthm,amscd,amstext}
\usepackage{mathtools}
\usepackage{exscale}
\usepackage{relsize}
\usepackage{mathrsfs}
\usepackage{tocloft}

@@

\renewcommand\cftsecfont{\normalsize}
\renewcommand\cftsecpagefont{\normalsize}
\renewcommand\cftsecafterpnum{\par}
\setlength{\cftbeforesecskip}{0.3em}

\renewcommand\cftsubsecfont{\small}
\renewcommand\cftsubsecpagefont{\small}
\renewcommand\cftsubsecafterpnum{\par}

@@

\begin{center} %<<< Title
	\Large \textbf{\textsf{
		Metrics and Algorithms for Evolving Social Networks}} \\[1.2em]
	\normalsize 
		Pufan He\upper{1}, Yichao Zhou\upper{2}, Qiwei Feng\upper{3},
		Yu Yan\upper{4}, Qingyang Li\upper{5} and Xin Xing\upper{6}\\[1em]
	\small
	\begin{tabular}{*{3}{>{\centering}p{.3\textwidth}}}
		\upper{1}\small\href{mailto:hpfdf@126.com}{hpfdf@126.com} &%
		\upper{2}\href{mailto:broken.zhou@gmail.com}{broken.zhou@gmail.com} &%
		\upper{3}\href{mailto:gdfqw93@163.com}{gdfqw93@163.com} \tabularnewline
		\upper{4}\href{mailto:whyvine@hotmail.com}{whyvine@hotmail.com} &
		\upper{5}\href{mailto:591527324@qq.com}{591527324@qq.com} &
		\upper{6}\href{mailto:823291634@qq.com}{823291634@qq.com}
	\end{tabular} \\[1em]

	\small Institute for Interdisciplinary Information Sciences,
	Tsinghua University \\[1.5em]
\end{center} \par %>>>

\begin{abstract}
We address the dynamic properties of typical social networks, in which person
is considered as vertex while relation is considered as edge. We suppose the
evolution of a social network overtime only includes bidirectional new
connections between existing or newly created nodes, and we assume the graph
will evolve as a typical social network. We study the centrality and activity
metrics for nodes in such graphs by regulate a series of reasonable properties
the metrics should satisfy. We then formally define our metrics and give their
mathematical analysis. We have developed a practical based framework to
maintain the evolving large-scale network and the algorithm to compute our
metrics with preferable time and space consumption, including historical
queries. Finally, we put the result of experiment with a couple of authentic
data.

\smallskip
\noindent \textbf{Keywords:} social network, dynamic graph, centrality,
activity, algorithm.
\end{abstract}
\tableofcontents
\newpage

\section{Introduction}
% TODO
\subsection{Dynamic Metrics}
% TODO
\subsection{Algorithms}
% TODO
\section{Evolving Social Network}
% TODO
\subsection{Definition}
% TODO
\subsection{Properties}
% TODO
\section{Centrality and Activity}
% TODO
\subsection{Desiderata}
% TODO
\subsection{Design and Analysis}
% TODO
\section{Algorithms}
% TODO
\subsection{Maintaining the basic graph structure}
% TODO
\subsection{Historical Queries}
% TODO
\subsection{Computing Metrics}
% TODO
\subsection{Mining Significant Data}
% TODO
\subsection{Optimization and Parallelizability}
% TODO
\section{Experiment}
% TODO
\section{Conclusion and Perspective}
% TODO
\nocite{*}
\bibliography{paper.bib}
\end{document}
